Notes on Control Plane Inference

### 2021-03-29 inference.tex
choose-> havoc
fix note

% commands
\newcommand{\assert}{\mathop{\mathsf{assert}}}
\newcommand{\assume}{\mathop{\mathsf{assume}}}
\newcommand{\apply}{\mathsf{apply}}
\newcommand{\choiceop}{\rotatebox[origin=c]{90}{$\sqsubset\!\!\!\sqsupset$}}
\newcommand{\choice}{\mathbin{\choiceop}}
\DeclareMathOperator*{\bigchoice}{\scalerel*{\choiceop}{\sum}}
\renewcommand{\choose}[2]{\mathop{\mathsf{choose}~#1~\mathsf{from}~#2~\mathsf{in}}}
\newcommand{\SKIP}{\mathsf{skip}}

@@

\begin{figure}
  \[\begin{array}{l>{\iff}cl}
  \satisfy \sigma \pkt \mu \FALSE && \textit{pigs fly} \\
  \satisfy \sigma \pkt \mu b_1 \Rightarrow b_2 &&
  \notsatisfy \sigma \pkt \mu  b_1~\textit{or}~
  \satisfy \sigma \pkt \mu b_2\\
  \satisfy \sigma \pkt \mu e_1 = e_2 &&
  \edenote{e_1}~\pkt~\mu = \edenote{e_2}~\pkt~\mu, \qquad
  \text{(note strict semantics)} \\
  \satisfy \sigma \pkt \mu \forall \rho \in t. ~b &&
  \forall r \in \sigma(t.\id).
  \satisfy \sigma \pkt {\mu\{\rho \mapsto r\}} b
  \end{array}
  \]
  \todo[inline]{Clarify $\error$ states}
  \todo[inline]{@Nate I know you wanted a standard satisfaction relation, but this was easier to think about in the context of the domain. The difference boils down to a naming convention}
  \caption{Satisfaction for $\BExpr$.}
  \label{fig:bool-satis}
\end{figure}

>>>>

% commands
\newcommand{\assert}{\mathop{\mathsf{assert}}}
\newcommand{\assume}{\mathop{\mathsf{assume}}}
\newcommand{\apply}{\mathsf{apply}}
\newcommand{\choiceop}{\rotatebox[origin=c]{90}{$\sqsubset\!\!\!\sqsupset$}}
\newcommand{\choice}{\mathbin{\choiceop}}
\DeclareMathOperator*{\bigchoice}{\scalerel*{\choiceop}{\sum}}
\renewcommand{\choose}[2]{\mathop{\mathsf{havoc}~#1~\mathsf{from}~#2~\mathsf{in}}}
\newcommand{\SKIP}{\mathsf{skip}}

@@

\begin{figure}
  \[\begin{array}{l>{\iff}cl}
  \satisfy \sigma \pkt \mu \FALSE && \textit{pigs fly} \\
  \satisfy \sigma \pkt \mu b_1 \Rightarrow b_2 &&
  \notsatisfy \sigma \pkt \mu  b_1~\textit{or}~
  \satisfy \sigma \pkt \mu b_2\\
  \satisfy \sigma \pkt \mu e_1 = e_2 &&
  \edenote{e_1}~\pkt~\mu = \edenote{e_2}~\pkt~\mu, \qquad
  \text{(note strict semantics)} \\
  \satisfy \sigma \pkt \mu \forall \rho \in t. ~b &&
  \forall r \in \sigma(t.\id).
  \satisfy \sigma \pkt {\mu\{\rho \mapsto r\}} b
  \end{array}
  \]
  \todo[inline]{Clarify $\error$ states} \todo[inline]{A goal here is to have a
    standard (i.e. single-model) satisfaction relation, but this was easier to
    think about in the context of the domain (esp. with scoped havoc). The
    difference boils down to a naming convention}
  \caption{Satisfaction for $\BExpr$.}
  \label{fig:bool-satis}
\end{figure}
